Strong lensing selection effects

### 2022-07-13 paper/seleff.tex
new figure 3

If no counter-image is detected, however, it can be difficult to distinguish such

For instance, it can be difficult to distinguish a single arc with no detected counter-image from a merging set of three images

This is because it is not always

>>>>

\begin{figure*}
\includegraphics[width=\textwidth]{footprints.eps}
\caption{
Criterion used to classify lensed images of extended sources.
}
\end{figure*}
%__________________________________________________________________
